Hyperspectral tree defoliation modeling with a focus on feature-selection and model interpretation

### 2019-06-28 code/98-paper/journal/manuscript.tex
add todos
update methods sections

@@

\paragraph{Ensuring a fair weighting in the ensemble}
Filter methods can be grouped into classes: Correlation based, entropy based, linear and non-linear methods.
It is important to not give certain classes too much weight in the ensemble as otherwise the final result will be biased.
This was taken care of by comparing the linear correlations of all generated filter values for each method against each other.
In case filters showed high correlations with each other, these were not included into the ensemble filter.
The goal was to create an ensemble filter showing low to medium correlations with each other.

@@

% I grouped these two since we focus on filter methods in this study - or is this already a bit biased towards filter methods?
\subsubsection{Wrapper methods and PCA}

@@

@@

For the filter methods, the percentage of features was optimized as a hyperparameter.
The number of main components was tuned for the \ac{PCA} based benchmarking experiments.

>>>>

% TODO: Mention the use of mtry.pow
% TODO: Explain the binning in the FSelectorfilters
% TODO: Explain that we used Spearman cor in the corrplot

@@

\paragraph{Ensuring a fair weighting in the ensemble}
Filter methods can be grouped into classes: Correlation based, entropy based, linear and non-linear methods.
It is important to not give certain classes too much weight in the ensemble as otherwise the final result will be biased.
This was taken care of by calculating the rank correlations (Spearman's correlation) of the generated feature rankings of all methods against each other.
In case filters showed high correlations with each other, these were not included into the ensemble filter.
This ensures that the ensembe filter is not biased towards a certain group of methods yielding highly similar rankings.

@@

% I grouped these two since we focus on filter methods in this study - or is this already a bit biased towards filter methods?

\noindent Filter method "information gain" is by creation only defined for class responses:

\begin{equation}
	H(Class) + H(Attribute) - H(Class, Attribute)
\end{equation}

where $H$ is the conditional entropy of the response variable (class) or the feature (attribute), respectively.
To be able to use this method with a numeric response, the variable is discretized into equal bins and treated as a class variable.
While the number of bins can be treated as a hyperparameter of the filter method, the default of the R package implementation of \texttt{$n_{bin}$ = 5} was used after rank correlations of > 0.9 for different bin sizes have been explored.

\subsubsection{Wrapper methods and PCA}

@@

\subsubsection{Calculation of the model's feature importance}

\noindent A permutation-based feature importance estimation was done for the best algorithm of each feature set and filter method, respectively.
This method caluclates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the loss in the used error measure will be, reflecting the importance of the specific feature for the current model.

\subsubsection{Linking feature importance to wavelength regions}
\noindent For ecological interpretation purposes we linked the ten most important indices of the winning models for each feature set to the spectral regions of the hyperspectral data.
For feature set HR and NRI a direct linking to the respective bands of the hyperspectral sensor was done.
For the vegetation indices all bands covered by the spectral range of calculated vegetation indices were counted and summed up.

@@

For the filter methods, the percentage of features was added to the models as a hyperparameter.
The number of main components was tuned for the instances which used \ac{PCA} instead of filtering.
Random Forest hyperparameter \texttt{$m_{try}$} was transformed from taking absolute values to a relative parameter depending on the number of tasks: $p^{m_{try}}$, where $p$ is the number of features.
This was necessary to ensure that \texttt{$m_{try}$} was not chosen out of bounds during tuning:
After the filtering, only a subset of features of the task is used for optimizing the models hyperparameters.
The size of this subset is always different since the number of features is also optimized.
Hence, the value of  \texttt{$m_{try}$} needs to be created flexible based on the number features.
